r5r: Rapid Realistic Routing with R5 in R

### 2020-09-18 r-package/paper2020/paper2020.Rmd
updates visualization paper section

### visualize results

`detailed_itineraries()` output is a `sf` object, which means that each trip 
segment is associated to a spatial geometry that can be plotted with common `R` 
packages, such as `ggplot2`. The package also offers a handy 
`street_network_to_sf()` function that extracts the OSM street network used in 
the routing as a `sf` object and can be used to provide geographic context for 
the visualization.

@@

>>>>

### Visualize results

`detailed_itineraries()` output is a `sf` object, which means that each trip 
segment is associated to a spatial geometry that can be plotted with common `R` 
packages, such as `ggplot2`. The package also offers a handy 
`street_network_to_sf()` function which extracts the OSM street network used by 
R<sup>5</sup> as a `sf` object and that can be used to provide geographic 
context for the visualization.

@@

The picture above can be used to compare the walking-only to the walking and 
transit itineraries between each origin/destination pair. Given that the sample 
`GTFS.zip` file includes only very few public transport routes, the resulting 
plot picture some odd scenarios, such as a fairly lengthy circular-like bus 
route, in the leftmost facet, and a very long walking access trip to the bus, 
in the rightmost facet.
